---
title: "Dataset 1"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Johnny Chapman
Hersh
MGSC 310

## Load Packages

```{r packages}
library(readr)
library('tidyverse')
library('ggthemes')
```

### Question A:
A note on directories. To see the curent working directory – execute the code getwd(). Let’s set our current working directory to the current location of our project file. This should happen by default if we are using R project files.


```{r}
getwd()
#setwd("C:/Users/johnnychapman/Desktop/Chapman/FALL19/MGSC310")
```

### Question B:
Download the Top 5000 movies on IMDB from the following link: 


```{r}
movies <- read.csv("Datasets/movie_metadata.csv")
```


### Question C:
What are the dimensions of the dataset? Programatically determine this using a function.


```{r}
dim(movies)
```


### Question D:
What are the names of the variables in the data set? Hint: use the function names here.


```{r}
names(movies)
```


### Question E:
Use the package ggplot2 to create a scatterplot of IMDB on the x-axis and movie budgets on the y-axis.

```{r}
ggplot(movies, aes(x = imdb_score, y = budget)) +
  geom_point() +
  labs(x = "IMDB Score", y = "Movie Budget", title = "IMDB Score and Movie Budget") + 
  theme_minimal()
```


### Question F: 
It looks like there are some outliers in terms of budget. The highest budget movie of all time was Pirates of the Caribbean: On Stranger Tides which cost 387.8m. Any movies with a budget higher than this must be a data anomaly. Run the code below to remove rows of movies which cost more than 400m to produce.
Now how many movies do we have in our data set?


```{r}
movies <- movies %>% filter(budget < 400000000) 
dim(movies) 
```
There are 4539 Movies under $400 million in budget


### Question G: 
Use stat_smooth() to create a trendline to the above figure. Is there a relationship between IMDB score and budget?


```{r}
ggplot(movies, aes(x = imdb_score, y = budget)) +
  geom_point() +
  labs(x = "IMDB Score", y = "Movie Budget", title = "IMDB Score and Movie Budget") + 
  theme_minimal() +
  stat_smooth()
```


### Question H: 
Use facet_wrap() to create sub-plots of relationship between IMDB Score and Budget. (Note, within the function facet_wrap() use the option , scales = "free" to allow the x-axes and y-axes to vary per sub-plot.For which content ratings do we see the strongest relationship between budget and IMDB score?


```{r}
ggplot(movies, aes(x = imdb_score, y = budget)) +
  geom_point() +
  labs(x = "IMDB Score", y = "Movie Budget", title = "IMDB Score and Movie Budget") + 
  theme_minimal() +
  stat_smooth() + 
  facet_wrap(~content_rating, scales = "free")
```


From these graphs, the content rating that shows the strongest relationship between Budget and IMDB Score seems to be PG-13. It shows a slight, steady incline in movie rating as the overall budget increases. 

### Question I: 
Install the R package ggrides to produce ridgeline density plots of simplified genre plots using the code below.


```{r}
library('ggridges')
movies <- movies %>% 
  mutate(genre_main = unlist(map(strsplit(as.character(movies$genres),"\\|"),1)),
                            grossM = gross / 1000000,
                            budgetM = budget / 1000000)

ggplot(movies, aes(x = grossM, y = genre_main, fill = genre_main)) + 
  geom_density_ridges() + 
  scale_x_continuous(limits = c(0, 500)) +
  labs(x = "Box Office Gross (USD Millions)", 
       y = "Main Genre")
```


### Question J: 
In a series of graphs (at least two) explore the relationship between budget and gross.

```{r}
ggplot(movies, aes(x = grossM, y = budgetM)) +
  geom_point() + 
  geom_smooth() + 
  labs(x = "Box Office Gross (USD Millions)", y = "Movie Budget (USD Millions)", title = "Movie Budget and Gross in Millions")+
  theme_minimal()
```

This graph shows a positive increase in Box Office Gross and Movie Budget. 

```{r}
ggplot(movies, aes(x = budgetM, y = grossM)) +
  geom_point() + 
  geom_smooth() + 
  labs(x = "Movie Budget (USD Millions)", y = "Box Office Gross (USD Millions)", title = "Movie Budget and Gross in Millions") +
  theme_minimal()
```
This graph above does not show as strong first graph, but still shows a slight increase in Box office Gross with and increase in Movie Budget.



